Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification

### 2019-09-03 190410_Paper_ACPR/paper_v5_r3-1.tex
ACPR_paper: rev 7

\begin{document}
%
\title{Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification}
%
\titlerunning{Triplet Network adopting KAR Learning for Wi-Fi Signature Verification}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
%
\authorrunning{Y. Kwon et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
In this paper, we propose an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signals using a triplet network. 
To refine the triplet inputs for fast loss convergence, the kernel and the range space learning is adopted in order to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.

@@

In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is taking considerable interest with the development of the in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than the contact-based authentication systems.

@@

In this paper, we utilize the deep triplet network for identity verification based on Wi-Fi CSI signature signal. To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs. Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on L-2 distance comparison.

The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
\item Adopted the KAR space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in triplet network.
\item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
\end{itemize}

@@

\subsection{Triplet network}
% triplet network
Triplet network is a kind of metric learning model \cite{weinberger2006distance} which aims to learn useful representations by using the distance comparison \cite{hoffer2015deep}. It is widely used in person re-identification problems, which solves the problem of matching individual identities between camera images\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}. 
The distinction between classes is challenging in this task since the distinctive feature is relatively weak compared to the background features such as pose, hair and textures.

To address this problem, the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data. The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive (similar) data closer to the anchor (reference) data and keeping the negative (dissimilar) data away from the anchor data.

% optimize training
Since myriad combinations of the triplet pairs can be generated in the training set, training with all possible triplets is time-consuming and unnecessary. To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.
Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed. They utilized large mini-batch at each training iteration and selected the triplet based on the training network.
However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.

@@

The multilayer feedforward neural networks is generally trained by the gradient descent method and the backpropagation \cite{goodfellow2016deep}.
However, setting the learning parameters such as learning rate or momentum value is important to use the gradient descent method.

Recently, gradient-free learning framework based on series of the kernel and the range (KAR) space manipulation has developed \cite{toh2018learning,toh2018gradient}.
Since it is trained by linear equations, no learning parameters nor the iteration are needed to train the networks.
Using this novel framework, we can train multilayer feedforward neural networks with any numbers and size of layers.

@@

%% Methods
\section{Proposed system}

% Methods: System overview(Fig.1)
In this section, we propose an identify verification system based on the Wi-Fi based in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using triplet network. Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network~\cite{schroff2015facenet}.
Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from the each given anchor sample in the training dataset (item (a) in Fig.~\ref{fig1}).
Subsequently, the ConvNet structure in the triplet network (item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (item (c) in Fig.~\ref{fig1}).
The following subsections will show the details of the triplet mining using KAR space learning and the triplet network.

@@

% Methods: KAR learning
\subsection{Triplet mining using kernel and the range space learning}
According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for the faster loss convergence when training the triplet network.
The hardest positive sample denotes the positive sample whose distance to the anchor sample is the greatest (which is most likely to be misclassified as a negative sample) while the hardest negative sample denotes the negative sample whose distance to the anchor sample is the least (which is most likely to be misclassified as a positive sample). However, there is no information about which sample is the hard positive or negative before we train the network.

In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a pretraining network to mine the hard positive/negative samples from the given anchor sample. Since the KAR space learning has no iterative learning process, we can mine the triplet samples without training an another network with backpropagation process.

By training the KAR space network with the training samples, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network. Taking each training sample as an anchor sample $\mathbf{x}_{anc}$, to measure the distance between $\mathbf{x}_{anc}$ and other samples, we first need to train the KAR space learning structure $f\left(.\right)$ using whole training sample matrix $\mathbf{X}\in \mathbb{R}^{n\times m}$ as follows~\cite{toh2018gradient}:
\begin{equation}
    f\left(\mathbf{X}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}
where $\mathbf{X}$ is a stacked matrix of $m$ training sample vectors, $\mathbf{W}_{1}\in{\mathbb{R}}^{(n+1) \times h_{1}}$, $\mathbf{W}_{2}\in{\mathbb{R}}^{(h_{1}+1) \times h_{2}}$, $\mathbf{W}_{i}\in{\mathbb{R}}^{(h_{(i-1)}+1) \times n}$, $\mathbf{1}=\left[1,\dots,1\right]^{T}\in{\mathbb{R}}^{m \times 1}$ and $\sigma(.)$ is an activation function.

Following, the hard positive sample $\mathbf{x}_{pos}$ and the hard negative sample $\mathbf{x}_{neg}$ from the input anchor sample $\mathbf{x}_{anc}$ can be respectively selected among the positive samples and the negative samples as follows:
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{pos}\right)}} \right\|_2^2} \geq \mathrm{t}_{pos}, \label{pos}
\end{equation}
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{neg}\right)}} \right\|_2^2} \leq \mathrm{t}_{neg},\label{neg}
\end{equation}
where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the thresholds which make the sample harder. Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative samples instead of just using the hardest positive/negative samples since the hardest samples are likely to be outliers which degrade the training process of the triplet network.
We empirically set the $\mathrm{t}_{pos}$ to 75 percentile of L-2 distance and $\mathrm{t}_{neg}$ to 25 percentile of L-2 distance and the final $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ are randomly selected among the samples which match the equations.

@@

Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$. The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1. The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layer. Following, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
The output vectors from the fully-connected layer are finally transformed using the sigmoid function following with the L-2 normalization.

@@

The triplet loss function is proposed in \cite{hoffer2015deep} to train the triplet network.
For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping with the hard positive input sample $\mathbf{x}_{pos,i}$ and the hard negative input sample $\mathbf{x}_{neg,i}$ selected based on the KAR space learning. Generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, the positive and the negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.

Here, the triplet loss function is calculated by comparing the positive distance (L-2 distance between the anchor vector and the positive vector) and the negative distance (L-2 distance between the anchor vector and the negative vector) as follows:
\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),\label{triplet}
\end{equation} 
where N denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
The ConvNet structure using equation~\eqref{triplet} is thus trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.

@@

\section{Conclusion}
In this paper, we proposed an identity verification system based on the handwritten signature signals captured by the Wi-Fi CSI signal using a triplet network adopting the kernel and the range (KAR) space learning. 
The kernel and the range space learning was initially adopted in order to mine the distinctive triple inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compared with the baseline triplet network and the Siamese network.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{splncs04}
%\bibliography{mybibliography}
%

>>>>

\begin{document}
%
\title{Deep Triplet Network adopting the Kernel and the Range Space Learning for Wi-Fi Handwritten Signature Verification}
%
\titlerunning{Triplet Network adopting KAR Learning for Wi-Fi Signature Verification}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Young-Woong Kwon \and Jooyoung Kim \and Kar-Ann Toh}
%
\authorrunning{Y. Kwon et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
School of Electrical and Electronic Engineering, Yonsei University, 50 Yonsei-ro, Seodaemun-gu, Seoul 03722, Republic of Korea\\
\email{\{herokwon, harrykim, katoh\}@yonsei.ac.kr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
%The abstract should briefly summarize the contents of the paper in 15--250 words.
In this paper, we propose a system for identity verification based on the handwritten signature signals captured by the Wi-Fi CSI signals. 
The kernel and the range space learning is initially adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure is trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset show encouraging verification accuracy with faster training loss convergence comparing with the baseline triplet network and the Siamese network.

@@

In recent years, several behavioral biometric traits for identity authentication have been investigated in view of their rigid physical body independence~\cite{bailador2011analysis}. Among the behavioral biometrics, the signature-based user authentication~\cite{sanmorino2012survey,galbally2015line} is attracting considerable interest with the development of in-air signature recognition systems~\cite{jeon2012system,sesa2012information,malik20183dairsig}.
With the help of sensors such as the depth camera~\cite{malik20183dairsig} or mobile sensor~\cite{jeon2012system}, the in-air signature recognition system has lower spatial constraint in the signature acquisition process than the contact-based authentication systems.

@@

In this paper, we utilize the deep triplet network for identity verification based on the Wi-Fi CSI signature signal. To achieve not only the desired verification accuracy but also a fast training speed, we adopt the kernel and the range (KAR) space leaning~\cite{toh100,toh2018learning,toh2018analytic,toh2018gradient} in order to mine the distinctive triplet inputs. Subsequently, the triplet network utilizing the ConvNet structure as a feature extractor is trained based on the L-2 distance comparison.

The main contributions of our work can be summarized as follows:
\begin{itemize}
\item Proposal of a system for identity verification based on the Wi-Fi handwritten signature signals using a deep triplet network.
\item Adopted the kernel and the range (KAR) space learning in order to mine the distinctive triplet inputs which boost the convergence speed of the training loss in triplet network.
\item Provision of the experimental study on an in-house Wi-Fi handwritten signature signal dataset collected from 50 subjects.
\end{itemize}

@@

\subsection{Triplet network}
% triplet network
The triplet network is considered a metric learning based model~\cite{weinberger2006distance} which aims to learn useful representations by means of distance comparison~\cite{hoffer2015deep}. 
\textbf{It is often seen in person re-identification~
\cite{chen2017beyond,cheng2016person,ding2015deep,schroff2015facenet,wang2016joint}. Re-identification is an identification problem using the images/videos taken from a different camera~\cite{bedagkar2014survey}. The individual identities are matched based on identity discriminative features. In these problems, the distinction among the classes is challenging since the features are relatively weak compared to the background features. To address this problem, the triplet network optimizes the embedding training data space such that data points with the same identity are closer to each other than those with different identities~\cite{hermans2017defense}.}

\textbf{The triplet network receives triplet pairs as its input which is made from a combination of the input data. Since not all triplet samples are contribute to the training ~\cite{schroff2015facenet}, recent issues have highlighted which input pairs will be used for training. To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.}

\textbf{Recently, \cite{schroff2015facenet} adopted additional triplet mining process for the faster convergence speed. They utilized large mini-batch at each training iteration and selected the triplet based on the training network rather than the random sampling. However, this strategy needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs which burden the time.}

%the triplet network receives triplet data as an input, which consists of the anchor, positive and negative data. The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive (similar) data closer to the anchor (reference) data and keeping the negative (dissimilar) data away from the anchor data.
%.... (1. tell how the triplet network solves the problem and not unrelated parts of it. 2. Tell what further issues arise from triplet network?)

% optimize training
%Not clear and no link to above, rewrite this sentence.
%Since myriad combinations of the triplet pairs can be generated in the training set, training with all possible triplets is time-consuming and unnecessary. To optimize the training process by utilizing only some part of the triplet pairs, \cite{cheng2016person,ding2015deep,wang2016joint} generated triplet only from limited classes, which are randomly selected in each iteration.
%Recently, \cite{schroff2015facenet} adopted triplet mining strategy for the faster convergence speed. They utilized large mini-batch at each training iteration and selected the triplet based on the training network.
%However, they needed a few thousand exemplars of mini-batch in every training iteration to select the triplet pairs.

@@

The multilayer feedforward neural networks is generally trained by the gradient descent method based on backpropagation \cite{goodfellow2016deep}.
However, setting the learning parameters such as learning rate or momentum value is time consuming and yet important to arrive at reasonable solution.

Recently, a gradient-free learning framework based on the kernel and the range (KAR) space manipulation has been developed for multilayer network learning~\cite{toh2018learning,toh2018gradient}.
The learning method is grounded on linear algebra with neither learning parameters nor iteration are needed in training.

@@

%% Methods
\section{Proposed System}

% Methods: System overview(Fig.1)
In this section, we propose an identity verification system based on the Wi-Fi based in-air handwritten signature (which will be called Wi-Fi signature signals hereafter) using the triplet network~\cite{hoffer2015deep}. Fig.1 shows an overview of the proposed system utilizing the kernel and the range (KAR) space learning~\cite{toh2018learning,toh2018gradient} for the triplet mining and the triplet network.
Essentially, the KAR space projection learning is trained and utilized to generate the triplet input data by mining the hard positive and the hard negative samples from each given anchor sample in the training dataset (see item (a) in Fig.~\ref{fig1}).
Subsequently, the ConvNet structure in the triplet network (see item (b) in Fig.~\ref{fig1}) is trained with the mined triplet data based on the triplet loss function using L-2 distance comparison (see item (c) in Fig.~\ref{fig1}).
The following subsections describe the details of the triplet mining using KAR space learning and the triplet network.

@@

% Methods: KAR learning
\subsection{Triplet mining using kernel and the range space learning}
%1. Need to explain what is "hard" first.
%2. Also, need to explain "anchor sample" before using it.
% description of anchor sample
% loss convergence problem
% we need hard sample selection

\textbf{The triplet network receives triplet data as an input, which consists of the reference data (will be called anchor hereafter) and corresponding positive (same class with the anchor) and negative data (different class with the anchor). The objective function of the triplet network is to place the feature vectors in the appropriate separation space by putting the positive data closer to the anchor data and keeping the negative data away from the anchor data.}

According to \cite{schroff2015facenet}, it is important to select the hard positive and the hard negative samples from each given anchor sample for faster loss convergence when training the triplet network.
The hard positive sample denotes the positive sample whose distance to the anchor sample is the greater than others (which is most likely to be misclassified as a negative sample) while the hard negative sample denotes the negative sample whose distance to the anchor sample is the smaller (which is most likely to be misclassified as a positive sample). However, there is no information about which sample is hard positive or negative before we train the network.

In this work, we propose to adopt the kernel and the range (KAR) space learning (see Section~\ref{kar} for details) as a pretraining network to mine the hard positive/negative samples from the given anchor sample. Since the KAR space learning has no iterative learning process, we can mine the triplet samples without using the time consuming backpropagation training process.

By training the network with using the single shot KAR space learning method, we can calculate the L-2 distance between every training samples by using the output vector from the KAR space network. Taking each training sample as an anchor sample $\mathbf{x}_{anc}$, to measure the distance between $\mathbf{x}_{anc}$ and other samples, the trained network output given by:

\begin{equation}
    f\left(\mathbf{X}\right) = \sigma\left(\left[\mathbf{1},\sigma\left(\dots\left[\mathbf{1},\sigma\left(\left[\mathbf{1},\sigma\left(\mathbf{X}\cdot\mathbf{W}_{1}\right)\right]\mathbf{W}_{2}\right)\right]\dots\mathbf{W}_{(i-1)}\right)\right]\mathbf{W}_{i}\right),
\end{equation}

is used to generate the hard positive and hard negative samples.
The hard positive sample $\mathbf{x}_{pos}$ and the hard negative sample $\mathbf{x}_{neg}$ with respect to the anchor sample $\mathbf{x}_{anc}$ can be respectively to determined by:

\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{pos}\right)}} \right\|_2^2} \geq \mathrm{t}_{pos}, \label{pos}
\end{equation}
\begin{equation}
    {\left\| {{f\left(\mathbf{x}_{anc}\right)} - {f\left(\mathbf{x}_{neg}\right)}} \right\|_2^2} \leq \mathrm{t}_{neg},\label{neg}
\end{equation}

where $\mathrm{t}_{pos}$ and $\mathrm{t}_{neg}$ denotes the thresholds which determines whether a sample is hard positive/negative. Here we utilized equations~\eqref{pos} and~\eqref{neg} to select the hard positive/negative samples instead of just using the hardest positive/negative samples since the hardest samples are likely to be outliers which degrade the training process of the triplet network.
We empirically set the $\mathrm{t}_{pos}$ to 75 percentile of L-2 distance and $\mathrm{t}_{neg}$ to 25 percentile of L-2 distance and the final $\mathbf{x}_{pos}$ and $\mathbf{x}_{neg}$ are randomly selected among the samples which match the equations.

@@

Our ConvNet structure (item (b) in Fig~\ref{fig1}) for the network consists of $i$ convolutional layers $\mathbf{C}_{i}$ and one fully-connected layer $\mathbf{F}$. The number of convolutional filters to be trained in each layer is empirically chosen as $\{64, 128, ...,  2^{6+i}\}$, with fixed filter size of $3\times3$ and stride of 1. The Rectiﬁed Linear (ReLU) function as an activation function and the Max-pooling layer are applied between each convolutional layer. Subsequently, the features from the last convolutional layer are directly flattened into a vector before the fully-connected layer $\mathbf{F}$.
The output vectors from the fully-connected layer are finally transformed using the sigmoid function following with the L-2 normalization.

@@

The triplet loss function was first seen in \cite{hoffer2015deep} to train the triplet network.
For the $i_{th}$ anchor input sample $\mathbf{x}_{anc,i}$, the triplet input is generated by grouping the hard positive input samples $\mathbf{x}_{pos,i}$ and the hard negative input samples $\mathbf{x}_{neg,i}$ selected based on the KAR space learning. The generated triplet input $\left\{\mathbf{x}_{anc,i},\mathbf{x}_{pos,i},\mathbf{x}_{neg,i}\right\}$ is then respectively transformed to the anchor, the positive and the negative feature vectors $\left\{\mathbf{v}_{anc,i},\mathbf{v}_{pos,i},\mathbf{v}_{neg,i}\right\}$ with the ConvNet structure.

Here, the triplet loss function is calculated by comparing the positive distance (L-2 distance between the anchor vector and the positive vector) and the negative distance (L-2 distance between the anchor vector and the negative vector) as follows:

\begin{equation}
    loss = \sum_i^N max\left({ \left[ {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{pos,i}}} \right\|_2^2} - {\left\| {{\mathbf{v}_{anc,i}} - {\mathbf{v}_{neg,i}}} \right\|_2^2}  + \alpha \right]}, 0 \right),\label{triplet}
\end{equation}

where $N$ denotes the size of the mini-batch, ${\left\| . \right\|_2^2}$ denotes the L-2 distance and $\alpha$ denotes the preset margin.
The ConvNet structure using equation~\eqref{triplet} is thus trained to maximize the gap between the positive distance and the negative distance which should be larger than the margin $\alpha$.

@@

\section{Conclusion}
In this paper, we proposed a system for identity verification based on the handwritten signature signals captured by the Wi-Fi CSI signals. 
The kernel and the range space learning was initially adopted for refining the triplet inputs for fast loss convergence by mining the distinctive inputs from the training Wi-Fi signature signals. 
Subsequently, the triplet network utilizing the ConvNet structure was trained with the mined triplet inputs based on L-2 distance comparison. 
Our experiments on an in-house Wi-Fi handwritten signature signal dataset showed encouraging verification accuracy with faster training loss convergence compared with the baseline triplet network and the Siamese network.
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
%\bibliographystyle{splncs04}
%\bibliography{mybibliography}
%
